Kindly Bent to Free Us

### 2019-07-04 kindly/lang.tex
Start explanation for borrow and regions.

\begin{figure}[!h]
  \centering
  \begin{subfigure}{0.4\linewidth}
    \begin{mathpar}
      \ruleSDRegion
    \end{mathpar}
    \caption{The {\sc Region} rule}
  \end{subfigure}\hfill
  \begin{subfigure}{0.6\linewidth}
    \centering
    \begin{tabular}
      {@{}>{$}r<{$}@{ $\Lleftarrow$ }
      >{$}c<{$}@{ $\rightsquigarrow_n^{x}$ }
      >{$}l<{$}
      r}

@@

      (\kaff_n\lk k\lk\kaff_\infty)
      &\svar[\MBORROW]{x}{\tau}^n
      &\bvar{\borrow[\MBORROW]{x}}{\borrowty[\MBORROW] k{\tau}}
      &Mut
    \end{tabular}
    \caption{Borrowing rules for bindings}
  \end{subfigure}
\end{figure}

>>>>

In order to provide good support for imperative programming, \affe allows
to borrows a resource. Such borrows are constrained to a given
region.
In order to support such features, we differentiate several sorts of
bindings in typing environments.
The grammar of type environment (noted $\E$) is shown in \cref{grammar:env}.
On top of the traditional type and value bindings, noted respectively
$\bvar{\tvar}{\kschm}$ and $\bvar{x}{\schm}$, we also consider two new
bindings.
Borrow bindings $\bvar{\borrow{x}}{\borrowty{k}{\tau}}$ which indicates
that the borrow $\borrow{x}$ can be used directly, as implemented
by the rule {\sc Borrow} in \cref{selectrules:borrow}
Suspended bindings $\svar{x}{\schm}^n$ indicates that $x$ is alive, but
can not be used immediately.
In order to use a suspended binding for the variable $x$,
we need to enter a \emph{region} associated with $x$,
as shown in the {\sc Region} rule.

\TODO{Explain region rule}

\begin{figure}[!h]
  \centering
  \begin{mathpar}
    \ruleSDBorrow

    \ruleSDRegion
  \end{mathpar}
  \caption{The {\sc Borrow} and {\sc Region} rules}
  \label{selectrules:borrow}
  \vspace{1em}

  \begin{minipage}{0.35\linewidth}
    \begin{align*}
      \htag{Type environments}
      \E &::=\ \Eempty \mid \E;B\\
      \htag{Bindings}
      B &::=\ \bnone \tag{Empty} \\
      &\mid \bvar{x}{\schm}\tag{Variables}\\
      &\mid \bvar{\borrow{x}}{\borrowty{k}{\tau}}\tag{Borrows}\\
      &\mid \svar{x}{\schm}^n \tag{Suspended}\\
      &\mid \bvar{\tvar}{\kschm}\tag{Types}
      % |&\ \tydecl{t}{\kschm}{K}{\tau}\tag{Type Declaration}\\
    \end{align*}
    \caption{Type environments}
    \label{grammar:env}
  \end{minipage}\hfill
  \begin{minipage}{0.6\linewidth}
    \centering
    \begin{tabular}
      {@{}>{$}r<{$}@{ $\Lleftarrow$ }
      >{$}c<{$}@{ $\rightsquigarrow_n^{x}$ }
      >{$}l<{$}
      r}

@@

      (\kaff_n\lk k\lk\kaff_\infty)
      &\svar[\MBORROW]{x}{\tau}^n
      &\bvar{\borrow[\MBORROW]{x}}{\borrowty[\MBORROW] k{\tau}}
      &Mut
    \end{tabular}
    \caption{Borrowing rules for bindings}
  \end{minipage}
\end{figure}
